---
title: "Final Project Lines"
format: pdf
editor: visual
---

```{r}
library(readr)
```

```{r}
library(tidyverse)
```

```{r}
data <- read_csv("Trimmed Down Durham Schools.xlsx - Sheet1.csv")
```

Error: 'Trimmed Down Durham Schools.xlsx - Sheet1.csv' does not exist in current working directory ('C:/Users/lucas/Documents/plan372/Final Project').

|     |                                                                                                                                                     |
|----------:|-------------------------------------------------------------|
| 6\. | stop("'", path, "' does not exist", if (!is_absolute_path(path)) { paste0(" in current working directory ('", getwd(), "')") }, ".", call. = FALSE) |

|     |                  |
|----:|------------------|
| 5\. | check_path(path) |

|     |                                                                                             |
|-----------:|------------------------------------------------------------|
| 4\. | (function (path, write = FALSE) { if (is.raw(path)) { return(rawConnection(path, "rb")) ... |

|     |                                                                                                                                                                                                                                                                                                  |
|----------:|-------------------------------------------------------------|
| 3\. | vroom\_(file, delim = delim %\|\|% col_types\$delim, col_names = col_names, col_types = col_types, id = id, skip = skip, col_select = col_select, name_repair = .name_repair, na = na, quote = quote, trim_ws = trim_ws, escape_double = escape_double, escape_backslash = escape_backslash, ... |

|     |                                                                                                               |
|-----------:|------------------------------------------------------------|
| 2\. | vroom::vroom(file, delim = ",", col_names = col_names, col_types = col_types, col_select = { { col_select ... |

|     |                                                           |
|----:|-----------------------------------------------------------|
| 1\. | read_csv("Trimmed Down Durham Schools.xlsx - Sheet1.csv") |

```{r}
colnames(data)
```

```{r}
data$Library_Y <- ifelse(data$'Library Distance' == "Y", 1, 0)
```

```{r}
data$Police_Response_Y <- ifelse(data$`Police Response` == "Y", 1, 0)
```

```{r}
data <- within(data, {  category_code_E <- ifelse(category_code == "E", 1, 0)
  category_code_H <- ifelse(category_code == "H", 1, 0)
  category_code_M <- ifelse(category_code == "M", 1, 0)})
```

```{r}
model1 <- lm(Library_Y ~ Grade, data = data)
summary(model1)
```

```{r}
model2 <- lm(Library_Y ~ Grade + category_code_E + category_code_M, data = data)
summary(model2)
```

```{r}
model3 <- lm(Library_Y ~ Grade + category_code_E + category_code_M + Police_Response_Y, data = data)
summary(model3)
```

```{r}
model_lpm <- lm(Library_Y ~ Grade, data = data)
summary(model_lpm)
```

```{r}
library(ggplot2)
```

```{r}
ggplot(data, aes(x = Grade, y= Library_Y)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Linear Probability Model: School Grade vs. Library Within Walking Distance", 
       x= 'School Grade',
       y = "Library Within Walking Distance (Y=1, N=0)")
```

```{r}
model_grade <- lm(Grade ~ Police_Response_Y + category_code_E + category_code_M + Library_Y, data = data)
summary(model_grade)
```

```{r}
modelgrade2 <- lm(Grade ~ Library_Y + category_code_E + category_code_M, data = data)
summary(modelgrade2)
```

```{r}
model1 <- lm(Grade ~ Library_Y, data = data)
summary(model1)
```
